---
date: "2018-09-09T00:00:00Z"
draft: false
lastmod: "2018-09-09T00:00:00Z"
linktitle: Links
menu:
  links:
    name: Links
    weight: 20
summary: Links and resources for Shiny, JavaScript, HTML, and CSS.
title: Awesome Web Dev in R
toc: false
type: docs
weight: 100
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(htmltools.dir.version = FALSE)
```

This is a big list of links to
articles,
blog posts,
JavaScript and CSS libraries,
online learning resources,
notes,
and so much more
that I found interesting while working on this workshop.

At the moment, I'll be honest: it's a bit of a mess.
But I hope to curate the list and add better search functionality
that will make it more usable in the future.

For now, I hope you find something helpful or interesting!

```{r echo=FALSE}
library(tidyverse)
library(glue)

links <- read_csv("~/Dropbox/Projects/js4shiny/js4shiny-workshop/static/resources-links.csv")

url_pattern <- "((https?|ftp|file)://)?([\\w\\d.-]+)\\.([a-zA-Z.]{2,6})([-/.a-zA-Z0-9]+)*/?"

titleCase <- function(x) {
	substr(x, 1, 1) <- toupper(substr(x, 1, 1))
	x
}

recode_groups <- c(
  css = "CSS",
  api = "API",
  es6 = "ES6",
  html = "HTML",
  js = "JS",
  pwa = "PWA",
  svg = "SVG",
  json = "JSON",
  jslib = "JS Library",
  vscode = "VS Code",
  "web-components" = "Web Components",
  "state-of-web-dev" = "State of Web Dev",
  rmarkdown = "R Markdown"
)

links %>%
	select(url = original_url, group, title, description) %>%
	# slice(1:5) %>%
	mutate(
		url_parts = map(url, str_match, pattern = url_pattern),
		url_slug = map_chr(url_parts, ~ glue("{.x[4]}.{.x[5]}")),
		url = map2_chr(url, url_slug, ~ htmltools::tags$a(href = .x, .y) %>% format()),
		group = trimws(group),
		group = map(group, ~ str_split(.x, pattern = " ")[[1]]),
		group_first = map_chr(group, `[`, 1),
		group_first = recode(group_first, !!!recode_groups),
		group_first = titleCase(group_first),
		group_first = recode(group_first, Jquery = "jQuery"),
		group = map_chr(group, ~ map(.x, ~ {
			htmltools::tags$span(class = "awesome-link-group-tag", .x) %>% format()
		}) %>% paste(collapse = " "))
	) %>%
	select(group_first, group, title, description, url) %>%
	group_nest(group_first) %>%
	purrr::pmap(function(group_first, data) {
		htmltools::tagList(
			htmltools::tags$h3(group_first),
			purrr::pmap(data, function(group, title, description, url) {
				htmltools::tags$li(
					class = "awesome-link",
					title,
					htmltools::HTML(glue("({url})")),
					if (!is.na(description)) htmltools::tags$div(
						class = "awesome-link-description",
						description
					),
					htmltools::tags$div(
						class= "awesome-link-groups",
						htmltools::HTML(group)
					)
				)
			}) %>%
				htmltools::tags$ul(class = "awesome-links", .)
		)
	}) %>%
  htmltools::tagList()
```


```{css echo=FALSE}
.awesome-links {
  padding-left: 0;
}

.awesome-link {
  list-style: none;
  margin-top: 1em;
  line-height: 1.5;
  border-color: var(--text-lighter);
  border-width: 1px;
  border-style: solid;
  padding: 0.5em 1em;
  position: relative;
  padding-right: 33%;
}

.awesome-link-group-tag {
  /* border: 1px solid var(--dark-blue); */
  border: 1px solid var(--green);
  background: var(--green-o10);
  padding: 0.05em 0.25em;
  border-radius: 3px;
  display: inline-block;
}

.awesome-link-description {
  color: var(--text-med);
  margin-top: 0;
  line-height: 1;
  margin-bottom: 0.25em;
}

.awesome-link-groups {
  position: absolute;
  right: 0.5em;
  top: 0.5em;
}

@media screen and (max-width: 530px) {
  .awesome-link {
    padding-right: 1em;
    font-size: 1.25em;
  }
  .awesome-link-groups {
    position: static;
    margin-top: 0.5em;
    margin-bottom: 0.3em;
    font-size: 0.9em;
  }
}
```